Estimating duration using survival analysis

### 2024-08-01 cis-perfect-testing.tex
Christl p.86 comment

Bayesian methods have been used for nest survival before~\autocite{heBayesiana,heBayesian,caoModeling} by augmenting the data with the unobserved times of infection.
The data augmentation approach creates a parameter for each detected infection.
This increases the dimensionality of the problem greatly, making it computationally infeasible with the large sample size of the CIS within the SRS.

>>>>

A related problem is estimating how long insect and bird nests survive for, as detected events are doubly interval censored and some are undetected.
In the context of nest survival, Bayesian methods have been by augmenting the data with the unobserved times of infection~\autocite{heBayesiana,heBayesian,caoModeling}.
The data augmentation approach creates a parameter for each detected infection.
This increases the dimensionality of the problem greatly, making it computationally infeasible with the large sample size of the CIS within the SRS.
